Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-04-09 SIR_manuscript.tex
change b to -b in Delta expression

Another representation of matrix $G_{11}$ in \eqref{G11} is as follows.
\begin{equation}
\label{G112}
G_{11} = \frac{\beta}{\gamma \, C} 
\left[ \begin {array}{c}  x\_n^* \\ x\_u^*  \end {array} \right]
\left[ \begin {array}{cccc} 
C-C_1, C-C_1-C_2\end {array} \right],
\end{equation}
where $C$ is in Eq. \eqref{eq:abc}, and $C_1$ and $C_2$ are 
\begin{align}
\label{eq:C12}
C =& (\omega+\gamma)(\gamma(\omega+\gamma)+(\omega\,p_I+\gamma)\,F_I)\\
C_1 =& (\omega+\gamma)(\theta\_w \, \gamma+\theta\_c\, \omega\, p_I) F_I,\\
C_2 =& (\omega+\gamma)\gamma^2\,\theta\_w+(\theta\_w-\theta\_c)\gamma\,p_I\,F_I.
\end{align}
$\Rnum$ is in the same form as in Eq. \eqref{R0}  $$\Rnum= \frac{\beta}{\gamma} (1-\Delta),$$
with equivalent but simplified $\Delta$ as
\begin{equation}
\label{eq:del2}
\Delta= \frac{C_1+C_2\,x\_n^*}{C}.
\end{equation}
The behavior of $\Rnum$ with respect to $\rho$ is determine by $\pro \Delta$
\begin{align}
\label{eq:dd2dr}
\pro \Delta=& \frac{1}{d} (a\,\rho^2+b\,\rho+c), \text{where}\\
a=& ((\omega+\gamma)\gamma -\omega \frac{w_I}{w_S} (\omega\,p_I+\gamma)) D_1,\\
b=& -2\gamma\omega(\omega+\gamma) D_1,\\
c=& \omega^2 (\omega+\gamma)^2 D_2,
\end{align}
with scaler $d>0$ (not effecting the sign of $\pro \Delta$) and $D_1$ and $D_2$ as 
\begin{align}
\label{eq:D1D2}
D_1=& (\omega+\gamma)\gamma\theta\_w+(\theta\_c-\theta\_w)\omega^2\,p_I\,\frac{w_I}{w_S}, \\
D_2=& (\omega\,\frac{w_I}{w_S}+\gamma)\gamma\theta\_w+\omega^2\,p_I\,\frac{w_I}{w_S}\,\theta\_c.
\end{align}

>>>>

Another representation of matrix $G_{11}$ in \eqref{G11} is as follows.
\begin{equation}
\label{G112}
G_{11} = \frac{\beta}{\gamma \, C} 
\left[ \begin {array}{c}  x\_n^* \\ x\_u^*  \end {array} \right]
\left[ \begin {array}{cccc} 
C-C_1, C-C_1-C_2\end {array} \right],
\end{equation}
where $C$ is in Eq. \eqref{eq:abc}, and $C_1$ and $C_2$ are 
\begin{align}
\label{eq:C12}
C =& (\omega+\gamma)(\gamma(\omega+\gamma)+(\omega\,p_I+\gamma)\,F_I)\\
C_1 =& (\omega+\gamma)(\theta\_w \, \gamma+\theta\_c\, \omega\, p_I) F_I,\\
C_2 =& (\omega+\gamma)\gamma^2\,\theta\_w+(\theta\_w-\theta\_c)\gamma\,p_I\,F_I.
\end{align}
$\Rnum$ is in the same form as in Eq. \eqref{R0}  $$\Rnum= \frac{\beta}{\gamma} (1-\Delta),$$
with equivalent but simplified $\Delta$ as
\begin{equation}
\label{eq:del2}
\Delta= \frac{C_1+C_2\,x\_n^*}{C}.
\end{equation}
The behavior of $\Rnum$ with respect to $\rho$ is determine by $\pro \Delta$
\begin{align}
\label{eq:dd2dr}
\pro \Delta=& \frac{1}{d} (a\,\rho^2-b\,\rho+c),
\end{align}
where
\begin{align}
\label{eq:abcd}
a=& ((\omega+\gamma)\gamma -\omega \frac{w_I}{w_S} (\omega\,p_I+\gamma)) D_1,\\
b=& 2\gamma\omega(\omega+\gamma) D_1,\\
c=& \omega^2 (\omega+\gamma)^2 D_2, \\
d=& \frac{\omega}{\gamma}(\omega+\gamma)\Big( \big( \gamma(\omega+\gamma)-\omega \frac{w_I}{w_S}(\omega\,p_I+\gamma)\big) \rho-\omega\gamma(\omega+\gamma) \Big)^2,
\end{align}
and $D_1$ and $D_2$ as 
\begin{align}
\label{eq:D1D2}
D_1=& (\omega+\gamma)\gamma\theta\_w+(\theta\_c-\theta\_w)\omega^2\,p_I\,\frac{w_I}{w_S}, \\
D_2=& (\omega\,\frac{w_I}{w_S}+\gamma)\gamma\theta\_w+\omega^2\,p_I\,\frac{w_I}{w_S}\,\theta\_c.
\end{align}
Note the following conditionbs and assumptions of the parameters of the model;
\begin{align}
\label{cond}
& \omega>0, \\
& 0 \leq \rho<\omega,\\ 
& 0 \leq \theta\_w \leq \theta\_c \leq 1, \\
& \frac{w_I}{w_S}\geq 1.
\end{align}
Given the parameter restrictions, we would like to determine the sign pattern of $\pro \Delta$ given the quadratic form of it in Eq. \eqref{eq:dd2dr}. Thus, it is important to know the sign of the coefficients $a$, $b$ and $c$ of the polynomial in Eq. \eqref{eq:dd2dr}. Note that with scaler $d>0$, it has no effect on the sign of $\pro \Delta$. Since $D_1\geq 0$ and $D_2\geq 0$, $b\geq 0$ and $c\geq 0$, sign of $a$ depends on the interplay between the involved parameters. Note that $D_1 \leq D_2$. (\todo{still working on}).
